Pollution, agricultural productivity, and development: Evidence from coal in plants in India\footnote{All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}

### 2023-01-13 draft/draft.Rmd
First draft!!

---
title: "Pollution, agricultural productivity, and development: Evidence from coal in plants in India^[thanks to...]"
author:
  - Joshua D. Merfeld^[KDI School of Public Policy and Management and IZA; merfeld@kdis.ac.kr]
date: "`r Sys.Date()`"
abstract: |
  | \noindent The rapid increase in population in India from the 1990s through the 2010s led to the rapid construction of new coal power plants throughout the country. Using this roll-out combined with randdom changes in wind direction, I document negative effects of pollution from coal power plants on agricultural productivity throughout the country. Results suggest this decrease may be driven by a decline in labor allocation of the oldest half of my sample, though I cannot rule out direct effects of pollution on land productivity. These impacts spill over into aggregate economic growth, as well; nightlight growth is slower following years of higher exposure to pollution.
  |
  | \textbf{\textit{Keywords}}: pollution, productivity, agriculture, labor, India
  | \textbf{\textit{JEL Codes}}: H40, I15, J22, O13, Q52, Q53

>>>>

---
title: "Pollution, agricultural productivity, and development: Evidence from coal in plants in India^[All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution_development]"
author:
  - Joshua D. Merfeld^[KDI School of Public Policy and Management and IZA; merfeld@kdis.ac.kr]
date: "`r Sys.Date()`"
abstract: |
  | \noindent The rapid increase in population in India from the 1990s through the 2010s led to the rapid construction of new coal power plants throughout the country. Using this roll-out combined with randdom changes in wind direction, I document negative effects of pollution from coal power plants on agricultural productivity throughout the country. Results suggest this decrease may be driven by a decline in labor allocation of the oldest half of my sample, though I cannot rule out direct effects of pollution on land productivity. These impacts spill over into aggregate economic growth, as well; nightlight growth is slower following years of higher exposure to pollution.
  |
  | \textbf{\textit{Keywords}}: pollution, productivity, agriculture, labor, India
  | \textbf{\textit{JEL Codes}}: H40, I15, J22, O13, Q52, Q53

### 2023-01-13 draft/draft.tex
First draft!!

\title{Pollution, agricultural productivity, and development: Evidence from coal in plants in India\footnote{thanks to\ldots{}}}
\author{Joshua D. Merfeld\footnote{KDI School of Public Policy and Management and IZA; \href{mailto:merfeld@kdis.ac.kr}{\nolinkurl{merfeld@kdis.ac.kr}}}}
\date{2023-01-13}

>>>>

\title{Pollution, agricultural productivity, and development: Evidence from coal in plants in India\footnote{All scripts used in this paper are publicly available on my GitHub page: github.com/JoshMerfeld/pollution\_development}}
\author{Joshua D. Merfeld\footnote{KDI School of Public Policy and Management and IZA; \href{mailto:merfeld@kdis.ac.kr}{\nolinkurl{merfeld@kdis.ac.kr}}}}
\date{2023-01-13}
